R for Clinical Study Reports and Submission

### 2023-05-23 tlf-baseline.qmd

There are many R packages that can efficiently summarize baseline information.
The [`table1`](https://github.com/benjaminrich/table1) R package is one of them.

@@

For simplicity, we only analyze `SEX`, `AGE` and, `RACE` in this example
using the `table1` R package. More details of the `table1` R package can
be found in the package
[vignettes](https://benjaminrich.github.io/table1/vignettes/table1-examples.html).

The `table1` R package directly creates an HTML report.

>>>>

There are many R packages that can efficiently summarize baseline information.
The [table1](https://github.com/benjaminrich/table1) R package is one of them.

@@

For simplicity, we only analyze `SEX`, `AGE` and, `RACE` in this example
using the table1 R package. More details of the table1 R package can
be found in the package
[vignettes](https://benjaminrich.github.io/table1/vignettes/table1-examples.html).

The table1 R package directly creates an HTML report.

### 2023-05-23 tlf-efficacy-km.qmd

::: {.rmdnote data-latex=""}
R packages such as
[visR](https://cran.r-project.org/package=visR) and
[survminer](https://cran.r-project.org/package=survminer)
can create more informative Kaplan-Meier plots.
Interested readers can find examples on their websites.
:::

>>>>

::: {.callout-note}
R packages such as
[visR](https://cran.r-project.org/package=visR) and
[survminer](https://cran.r-project.org/package=survminer)
can create more informative Kaplan-Meier plots.
Interested readers can find examples on their websites.
:::

### 2023-05-23 tlf-population.qmd

# Analysis population {#population}

@@

-   USUBJID: unique subject identifier
-   ITTFL: intent-to-treat population flag
-   EFFFL: efficacy population flag
-   SAFFL: safty population flag

@@

In Chapter \@ref(disposition), there are a few repeating steps to:

@@

```{r}
fmt_num <- function(x, digits, width = digits + 4) {
  formatC(x,
    digits = digits,
    format = "f",
    width = width
  )
}
```

@@

For example, we can compare the two versions of code to format the
percentage used in Chapter \@ref(disposition) and `fmt_num`.

@@

```{r}
rel_width <- c(2, rep(1, 3))
colheader <- " | Placebo | Xanomeline line Low Dose| Xanomeline line High Dose"
tbl_pop %>%
  # Table title
  rtf_title(
    "Summary of Analysis Sets", ## "Participants Accounting in Analysis Population" is a weird title for me. Merck uses this table title for CSR? 
    "(All Participants Randomized)"
  ) %>%
  # First row of column header
  rtf_colheader(colheader,
    col_rel_width = rel_width
  ) %>%
  # Second row of column header
  rtf_colheader(" | n (%) | n (%) | n (%)",
    border_top = "",
    col_rel_width = rel_width
  ) %>%
  # Table body
  rtf_body(
    col_rel_width = rel_width,
    text_justification = c("l", rep("c", 3))
  ) %>%
  # Encoding RTF syntax
  rtf_encode() %>%
  # Save to a file
  write_rtf("tlf/tbl_pop.rtf")
```

>>>>

# Analysis population {#sec-population}

```{r, include=FALSE}
source("_common.R")
```

@@

- USUBJID: unique subject identifier
- ITTFL: intent-to-treat population flag
- EFFFL: efficacy population flag
- SAFFL: safety population flag

@@

In @sec-disposition, there are a few repeating steps to:

@@

```{r}
fmt_num <- function(x, digits, width = digits + 4) {
  formatC(
    x,
    digits = digits,
    format = "f",
    width = width
  )
}
```

@@

For example, we can compare the two versions of code to format the
percentage used in @sec-disposition and `fmt_num()`.

@@

```{r}
rel_width <- c(2, rep(1, 3))
colheader <- " | Placebo | Xanomeline line Low Dose| Xanomeline line High Dose"
tbl_pop %>%
  # Table title
  rtf_title(
    "Summary of Analysis Sets",
    "(All Participants Randomized)"
  ) %>%
  # First row of column header
  rtf_colheader(colheader,
    col_rel_width = rel_width
  ) %>%
  # Second row of column header
  rtf_colheader(" | n (%) | n (%) | n (%)",
    border_top = "",
    col_rel_width = rel_width
  ) %>%
  # Table body
  rtf_body(
    col_rel_width = rel_width,
    text_justification = c("l", rep("c", 3))
  ) %>%
  # Encoding RTF syntax
  rtf_encode() %>%
  # Save to a file
  write_rtf("tlf/tbl_pop.rtf")
```
